Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2021-05-20 paper_io_sim.tex
Fixed typo in yaxis label in Fig 4-a, text edits

            This prototype does not simulate  bandwidth sharing and thus
            does not support concurrency: it is limited to single-threaded
            applications running on systems with a single-core CPU. We used
            this prototype for a first validation of our simulation model
            against a real sequential application running on a real system,
            and as a way to detect potential bugs in our implementation.
            The Python 3.7 source code is available at
            \url{https://github.com/big-data-lab-team/paper-io-simulation/tree/master/exp/pysim}.

@@

        Experiments were run on a dedicated cluster at
        Concordia University, with one login node, 9 compute nodes, and 4
        storage nodes connected with a 25 Gbps network. Each
        compute node has 2 $\times$ 16-core Intel(R) Xeon(R) Gold 6130 CPU
        @ 2.10GHz, 250~GiB of RAM, 6 $\times$ SSDs of 450~GiB each with the XFS
        file system, 378~GiB of tmpfs, 126~GiB of devtmpfs file system,
        CentOS~8.1 and NFS version 4. We used the \texttt{atop}
        and \texttt{collectl} tools to monitor and collect memory status
        and disk throughput. We cleared the page
        cache before each application run to ensure comparable
        conditions.

@@

            \begin{figure*}
                \begin{subfigure}{\linewidth}
                    \centering
                    \includegraphics[width=0.8\linewidth]{result/multi/figures/multi_local.pdf}
                \end{subfigure}
                \caption{Concurrent results with 3~GB files (\textit{Exp 2})}
                \label{fig:multi_local}
            \end{figure*}
            \begin{figure*}
                \begin{subfigure}{\linewidth}
                    \centering
                    \includegraphics[width=0.8\linewidth]{result/multi/figures/multi_nfs.pdf}
                \end{subfigure}
                \caption{NFS results with 3~GB files (\textit{Exp 3})}
                \label{fig:multi_nfs}
                \end{figure*}
        \subsection{Concurrent applications (Exp 2)}

>>>>

            This prototype does not simulate  bandwidth sharing and thus
            does not support concurrency. We used
            this prototype for a first validation of our simulation model
            against a real sequential application running on a real system,
            and as a way to detect potential bugs in our implementation.
            The Python 3.7 source code is available at
            \url{https://github.com/big-data-lab-team/paper-io-simulation/tree/master/exp/pysim}.

@@

        Experiments were run on a dedicated cluster at
        Concordia University, with one login node, 9 compute nodes, and 4
        storage nodes connected with a 25 Gbps network. Each
        compute node has 2 $\times$ 16-core Intel(R) Xeon(R) Gold 6130 CPU
        @ 2.10GHz, 250~GiB of RAM, 6 $\times$ SSDs of 450~GiB each with the XFS
        file system (no RAID enabled), 378~GiB of tmpfs, 126~GiB of devtmpfs file system,
        CentOS~8.1 and NFS version 4. We used the \texttt{atop}
        and \texttt{collectl} tools to monitor and collect memory status
        and disk throughput. We cleared the page
        cache before each application run to ensure comparable
        conditions.

@@

            \begin{figure*}
                \begin{subfigure}{\linewidth}
                    \centering
                    \includegraphics[width=\linewidth]{result/multi/figures/multi_local.pdf}
                \end{subfigure}
                \caption{Concurrent results with 3~GB files (\textit{Exp 2})}
                \label{fig:multi_local}
            \end{figure*}
            \begin{figure*}
                \begin{subfigure}{\linewidth}
                    \centering
                    \includegraphics[width=\linewidth]{result/multi/figures/multi_nfs.pdf}
                \end{subfigure}
                \caption{NFS results with 3~GB files (\textit{Exp 3})}
                \label{fig:multi_nfs}
                \end{figure*}
        \subsection{Concurrent applications (Exp 2)}
